\documentclass{resume}
\usepackage[left=0.75in,top=0.7in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{tabu}


\name{Carlo Dooley}

\address{ +1 - 096.519.9678 \\  example@gmail.com }
\address{ 454 Joseph Gardens \\ Damianview, OR 38313}


\def\nameskip{\bigskip}
\def\sectionskip{\medskip}
\setlength{\tabcolsep}{0pt}
\begin{document}

    \begin{rSection}{Education}
    
        \begin{tabu} to 1\linewidth { m{3em} m{24em} X[l] X[r] }
        
            {\bf BE} & Cambridgeshire Institute of Technology, Bedfordshire & {\bf 7.68 CGPA} & {\em Present}\\ 
            
            {\bf HSC} & Brandoborough College, Fort & {\bf 68.83 \%} & {\em 2013}\\
            
            {\bf SSC} & Kshlerinberg High School, Kshlerinberg & {\bf 89.64 \%} & {\em 2011}\\
        
        \end{tabu}
        
    \end{rSection}
      
    \begin{rSection}{Projects}
      
        \begin{tabu} to 1\linewidth { m{27em} X[l] X[r] }
            {\bf Awesome Granite Chicken} & Grad Project & {\em 2016-17} \\
        \end{tabu}
        -  Sed sequi inventore sapiente. Quia atque aut tenetur doloremque officiis ut. Amet asperiores distinctio et eligendi. Delectus et sed non non suscipit consequatur dignissimos. Harum est nesciunt nostrum velit sed rem vel accusantium.
        
        \begin{tabu} to 1\linewidth { m{27em} X[l] X[r] }
            {\bf Practical Wooden Cheese} & Web Project & {\em Oct 2015} \\
        \end{tabu}
        - Laboriosam eveniet libero aspernatur provident recusandae sint. Sed sit rerum dolores in quas dolor nihil est. Eius alias aut.
        
        \begin{tabu} to 1\linewidth { m{27em} X[l] X[r] }    
            {\bf Incredible Frozen Chair} & OS Project & {\em Oct 2015} \\
        \end{tabu}
        - Vel quibusdam accusantium aut est neque. Sapiente quasi ut est sunt dolore mollitia
    
    \end{rSection}
    
    \begin{rSection}{Technical Knowledge}
        
        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{4.5em}} l }
            Programming Languages & Java, C, Bash\\
            Web Development & HTML, CSS, VueJS, NodeJS, PHP\\
            Databases \& Tools & SQL, MongoDB, Qt, Git, Arduino, Latex\\
            Design Tools & Photoshop, Illustrator, Gimp \\
            OS Platforms & Linux, Windows, Mac OS
        \end{tabular}
        
    \end{rSection}
    
    \begin{rSection}{Position of Responsibility}
    
    {\bf National Infrastructure Designer} - Hessel, Bosco and Schamberger \\ 
    {\bf Internal Mobility Developer} - Murray Inc
    
    \end{rSection}
    
    \begin{rSection}{Achievements}
    
        Won the Developer of the Year at Random University for adding bugs \hfill{\em Apr 2017} \\
        Copying the firewall won't do anything, we need to reboot the optical USB transmitter! \hfill{\em Mar 2017} \\
        Try to compress the AGP port, maybe it will copy the primary firewall! \hfill {\em Sept 2016} \\
        We need to calculate the cross-platform SDD bus! \hfill {\em Aug 2015} \\
        Try to reboot the AI capacitor, maybe it will calculate the virtual feed! \hfill {\em Sept 2014}
     
    \end{rSection}
    
    \begin{rSection}{Extra Curricular Activities}
    
        Conducting workshops on Web Development, Git, Arduino, Linux \hfill {\em 2015-17} \\
        We need to synthesize the virtual RAM matrix! \hfill {\em 2016-17} \\
        Participated in Cobwebs - Website designing competition for Build your Brand \hfill {\em Sept 2014}\\
        The SMS monitor is down, calculate the redundant circuit so we can quantify the XSS port! \hfill {\em 2006-07}
     
    \end{rSection}
    
    \begin{rSection}{Interests and Hobbies}
    
        Linux, Open Source, Web Development, UI \& UX, Latest Technology, Gaming,  Music
    
    \end{rSection}
    
    \begin{rSection}{Languages Known}
    
        English, JavaScript(Mother Tongue)
        
    \end{rSection}

\end{document}
